### 2019-12-12 article_draft.tex
Made changes to intro

\sh{It is often of interest if any of a large number of candiate measurements are useful in predicting some outcome}. In genetics many candidate snips and their association with some outcome is often of interest. Many studies take measurements on a large number of biomarkers to see if any can predict medical outcomes such as the presence  or progression of a disease. While interest in the existence of an association between two variables has existed for years, the vast number of potential predictors creates new statistical challenges.  In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}. In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.  However, as mentioned above, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.  Even in the case with two covariates, a test with the above optimal property no longer exists.

To illustrate this, consider two tests with equal type one error rates. Both test the null that both of the two association measures $\psi_1$, $\psi_2$ are zero. The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.  When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.  Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.  Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).  These two factors make it difficult to define a test that performs well across all possible alternatives.  
% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.

>>>>

\sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}. In genetics many candidate snips and their association with some outcome is of interest. Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease. While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.  The vast number of potential predictors creates new statistical challenges to answering this less obvious question.

In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}. In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.  However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.  Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.

To illustrate this, consider two tests with equal type one error rates. Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero. The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.  When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.  Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.  Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).  These two factors make it difficult to define a test that performs well across all possible alternatives.  
% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.
